Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-09-02 docs/comments/comments.tex
nits

\noindent
{\bf Response:}
We are thankful to the reviewers for their thorough reviews.
We have revised our paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
Number wise answers to their specific
comments / suggestions / queries are as follows.\\

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
could be more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

@@

\noindent
{\bf Response:}
The 2nd reviewer has also indicated that
information flow control solutions
were missing from our study.
Our paper now includes six solutions
that follow this approach
including {\sc sif}~\cite{CVMA07},
Hails~\cite{GLSTMMR12}
and Aeolus~\cite{CPSPBCCSL12}
(see Subsection 5.3, Figure 2 and 3).
Nevertheless,
we did not include Ur/Web~\cite{C10b}
in our study because it is a static 
analysis mechanism
(recall that we only consider defenses
that prevent attacks when they take place).

>>>>

\noindent
{\bf Response:}
We are thankful to the reviewers for their thorough reviews.
We have revised our paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
In the following we provide answers to specific
comments/suggestions/queries.\\

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
they could become more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

@@

\noindent
{\bf Response:}
The 2nd reviewer has also indicated that
information flow control solutions
were missing from our study.
Our paper now includes six solutions
that follow this approach,
including {\sc sif}~\cite{CVMA07},
Hails~\cite{GLSTMMR12}
and Aeolus~\cite{CPSPBCCSL12}
(see Subsection 5.3, Figure 2 and 3).
Nevertheless,
we did not include Ur/Web~\cite{C10b}
in our study because it is a static 
analysis mechanism
(recall that we only consider defenses
that prevent attacks when they take place).
